Spatial Analysis

### 2021-10-29 Scripts/spatial_analisis.Rmd
saved top port data for future analysis

# Include coordinates
noaa_ports_complete <- top_ports %>% 
  left_join(noaa_ports,
             by = c("port_name", "state_postal"))

@@

# Save data for future analysis

write_csv(noaa_ports_complete,
          my_path("D","NOAA", name = "top_ports.csv")
          )

@@

top10_ports %>% 
  left_join(noaa_ports) %>% 
  ggplot() +
  geom_point(
    aes(
      x = lon,
      y = lat,
      shape = species_name, 
      color = species_name
    ),
    size = 5,
    alpha = 0.5
  )

@@

# Visual exploration of all together (o.k! )
ggplot() +
  geom_sf(data = eez_sf, aes()) +
  geom_sf(data = land_sf, aes(fill = state), alpha = 0.3) +
  geom_sf(data = state_sf, aes(color = state), fill = NA) +
  geom_point(data = ports_df, aes(x = lon, y = lat,
                                  shape = species_name), size = 3, alpha = 0.7) +
  scale_color_manual(values = state_pallet) +
  scale_fill_manual(values = state_pallet) +
  theme_dark() +
  coord_sf(ylim = c(33,48))

>>>>

# Include coordinates
noaa_ports_complete <- top_ports %>% 
  left_join(noaa_ports,
             by = c("port_name", "state_postal")) %>% 
  mutate(
    state_postal = str_to_upper(state_postal)
  )

@@

# Save data for future analysis
# write_csv(noaa_ports_complete,
#           my_path("D","NOAA", name = "top_ports.csv")
#           )

noaa_ports_complete

@@

noaa_ports_complete %>% 
  filter(tresh == "75th") %>% 
  ggplot() +
  geom_point(
    aes(
      x = lon,
      y = lat,
      shape = species_name, 
      color = species_name
    ),
    size = 5,
    alpha = 0.5
  )

@@

# Visual exploration of all together (o.k! )
ggplot() +
  geom_sf(data = eez_sf, aes()) +
  geom_sf(data = land_sf, aes(fill = state), alpha = 0.3) +
  geom_sf(data = state_sf, aes(color = state), fill = NA) +
  geom_point(data = subset(noaa_ports_complete, tresh == "75th"), aes(x = lon, y = lat,
                                  shape = species_name), size = 3, alpha = 0.7) +
  scale_color_manual(values = state_pallet) +
  scale_fill_manual(values = state_pallet) +
  theme_dark() +
  coord_sf(ylim = c(33,48))
